Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-24 review_article.Rmd

>>>>

# Conclusions

<!-- summary of mapping -->
This paper provides an overview of mapping practices as used for cancer atlases, and new approaches that could be adopted. The conventional approach is the choropleth map, and it is widely used. When there are small areas, as occurs in Australia where the population is concentrated on the coast, the information about cancer can be lost, and alternatives are needed. Making an inset can clarify congested regions but this breaks the viewers attention, because they need to shift focus from the map to the inset, and if there are many congested areas, many insets would be needed. The map alternatives, like cartograms and their variations, can be useful to allow the spatial distribution of cancer data to be digested.

<!-- statistics -->
There are many different statistics that are commonly used for display. The most basic is incidence rate, which is easy to understand. It is common to see relative rates in many maps which measure how far a region is above or below the average. The purpose of using a relative rate is, perhaps the desire to pinpoint the areas that need attention because they have higher than expected rates. However, we lose the incidence rate information and thus interpretability. A region might be much higher than average, but it may not be close to a health concern, because all regions have low incidence.

<!-- interaction -->
